---
title: "HW3_BaseRProgramming"
format: pdf
editor: visual
---

## Task 1 

### Part A: Read in data.txt file 


```{r}
library(tidyverse)
library(palmerpenguins)

data_v1 <- read_csv("/Users/alexiskolecki/Repos/Data/data.txt")
data_v1
```
We can not use this specific read_csv() to read this data since the data is seperated by semicolons and not commas or tabs. 

```{r}
data <- read_csv2("/Users/alexiskolecki/Repos/Data/data.txt")
data
```

### Part 2 : Read in data2.txt 

```{r}
data2 <- read_delim("/Users/alexiskolecki/Repos/Data/data2.txt", delim = '6',
                    col_types = "fdc")
data2
```

## Task 2 

### Part 1: Take a glimpse of the trailblazer data set to show that you have read in the data correctly 

```{r}
trailblazer <- read_csv("/Users/alexiskolecki/Repos/Data/trailblazer.csv")
trailblazer
```

### Part 2 : Pivot the data so that you have columns for player, game, location, points. Display the first five rows of your data set. 

```{r}
trailblazer_longer <- pivot_longer(trailblazer, cols = 2:11,names_to = "Games", values_to = "Points")
trailblazer_longer <- separate_wider_delim(trailblazer_longer, Games, delim ="_" ,
                                names = c("Games", "Location"))
                     
trailblazer_longer
```

### Part 3 : Which players scored more on average when playing at home verus away? 

```{r}
trailblazer_longer|> pivot_wider(names_from = Location, values_from = Points) |>
  group_by(Player)|>
  summarize(mean_home = mean(Home, na.rm = TRUE), 
            mean_away = mean(Away, 
          na.rm =TRUE), difference = mean_home - mean_away) |>
  arrange(desc(difference))
  

```
On average, Jusuf Nurkic scored more points at home than away through the first 10 games of the season. 

## Task 3

### Part A : Example the Errors in the code that co worker sent you 

Whats going on here? Explain the <NULL>, <dbl [52]> and <list> means. 

* There is an error being caused because thre are duplicate rows in the data file. 

* The <NULL> means that that spot in the table is empty and there are no values for this spot in the table.

* The <list> refers to a list object in R.

* The <dbl[52]> means a numeric data type that can be up to 52 values. 

### Part B : Recreate the Table

```{r}
penguins

penguins |>
group_by(species, island) |>
  summarise(count = n())|>
  pivot_wider(names_from = island, values_from = count)

```
## Task 4

### Replace NA with correct bill values

```{r}
penguins

penguins |>
mutate(bill_length_mm = case_when(is.na(bill_length_mm) & species == 'Gentoo' ~ 30,
                                  is.na(bill_length_mm) & species == 'Adelie' ~ 26,
                                  TRUE ~ bill_length_mm)) |> arrange(bill_length_mm)

```

